Kronos \& Krios: Evidence for accretion of massive, rocky planetary system in a sun-like pair

### 2017-06-08 paper/ms.tex
Trim down review section.

{\bf HD~20782/HD~20781:}
\citealt{Mack:2014aa} studied HD~20782/20781, two common proper motion G dwarf
stars (G2/G9.5) with a projected separation of $\sim9000$~AU (corresponding to
4.2\arcmin\ sky separation). Both stars in this system host close-in giant
planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$) \footnote{
  The two stars were monitored by \project{HARPS} campaign, and it has recently
  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
  within $\approx 0.35$~AU.}.
They found that the abundances of 15 elements between the two stars are
consistent with each other.
However, they argued that there is a moderately significant ($\sim 2\sigma$)
positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ in abundance of each star
{\it individually} with increasing \Tcondens\ for $\Tcondens>900$~K elements
(namely, Na, Mn, Cr, Si, Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O
of their measurements).
They interpreted that this slope may be evidence for accretion of
$10-20$~\mearth\ of H-depleted rocky material that were pushed in during giant
planet migration.

{\bf HAT-P-1:}
HAT-P-1 is a pair of G0 stars separated 11\arcsec\ apart in sky
with $\feh\approx0.15$.
The secondary star in the system is known to host one transiting giant planet
while no planet has been discovered around the primary star.
\citealt{Liu:2014aa} found that the two stars are identical in their
atmospheric composition: \feh\ is $0.146 \pm 0.014$ and $0.155 \pm 0.007$ for
the primary and secondary respectively, and $\Delta\elem{X}/\elem{Fe}$ is
consistent with zero for 23 elements measured with the mean error being
$0.013$~dex.
Based on this analysis, they concluded that the presence of close-in giant planet
does not necessarily lead to stellar atmospheric pollution of the host star.

{\bf HD~80606/HD~80607:}
A pair of G5 stars with super-solar metallicity ($\feh \approx 0.35$),
HD 80606/HD 80607, has been independently studied by
\citealt{Saffe:2015aa} and \citealt{Mack:2016aa} using the same KECK HIRES
spectra. HD 80606 hosts a giant planet with mass of $4~\mjupiter$ at $0.5$~AU
on a very eccentric ($e\approx0.95$) orbit while HD 80607 has no detected
planets.
Both studies have concluded that there is no significant
chemical difference between the two stars similar to the case of HAT-P-1.

{\bf XO-2N/XO-2S:}
The double star system XO-2 has received much attention due to
possibly the most robust and significant difference between the component stars
among those so far studied.
XO-2 is a pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
each hosting planet(s).
XO-2N hosts on giant planet while XO-2S is known to host two giant planets with
masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
0.15$) orbits at $<0.5$~AU.

The system was first analyzed by \citealt{Teske:2013aa}, who examined and found
essentially no significant difference in Fe, Ni, C, and O between the two
stars.
However, re-analysis of the system by the same authors using the same data in
\citealt{Teske:2015aa} found that the trend of $\Delta\elemH{X}$ with
\Tcondens\ varies significantly depending on the stellar parameters chosen in
their analysis. Both analyses were based on spectra
using Subaru High Dispersion Spectrograph at spectral resolution $R=60000$
covering $4450-5660$~\AA\ and $5860-7100$~\AA\ with S/N of $170-230$
(\citealt{Teske:2013aa}).

Independently, \citealt{Ramirez:2015aa} used Keck HIRES spectra ($R=67000$,
$4080-8300$~\AA) of the component stars with S/N of $350$ (in $5000-7500$~\AA)
to perform a differential abundance analysis.
They find that all 23 elements including Fe are enhanced in XO-2N
compared to XO-2S, and that the difference $\Delta\elemH{X}$ shows
a significant correlation with \Tcondens.
At low \Tcondens, volatile elements differ by $0.015$~dex
while the range of difference spans upto $0.1$~dex at $\Tcondens>1600$~K.
There are inconsistencies in the determination of stellar parameters
(\teff\ and \logg) between spectroscopic (based on Fe I/II lines)
and photometric analysis,
but the existence of correlation between $\Delta\elem{H}$ and
\Tcondens\ seems robust.

\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
giant planets around XO-2S, following a similar interpretation of
\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
In this scenario, forming planets in the protoplanetary disk are supposed to
``lock'' heavier elements to the core of gas giant planets as well as some
volatile elements in their envelopes. Then, the host star will accrete {\it
  gas} depleted in metals compared to their protostellar condition.
By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
of gas occurs in terms of how much mass is in the convective envelop then, they
can match the mass difference of gas giant planets around each star, which is
at least $1~\mjupiter$.
On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
Earth and CM chondrite-like material can explain the trend either as refractory
{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
refractory enhancement in XO-2N by late time accretion in which case the
complete opposite would be true.

%TODO: summarize Biazzo+ on XO-2
%Finally, \citealt{Biazzo:2015aa}

{\bf WASP-94A/WASP-94B:}
\citealt{Teske:2016aa} studied WASP-94A/WASP-94B, a pair of F8 and F9 stars
with super-solar metallicity ($\feh\approx 0.3$ for both stars). Both stars
host a hot Jupiter.
The planet hosted by WASP-94A is transiting with a misaligned, probably
retrograde circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little
more massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host
star.
With a claimed median uncertainty of $0.006$~dex among all elements, they
detected a depletion of volatile and moderately volatile ($\Tcondens < 1200$~K)
elements at $0.02$~dex level and an enhancement in refractory ($\Tcondens >
1200$~K) elements at $0.01$~dex level in WASP-94A relative to WASP-94B.
Excluding K, which is based on one strong line and largely affected by non-LTE
effect, their analysis shows a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$\footnote{
  %TODO: double check the following statement
  Note that the condensation
  temperature $\Tcondens$ used is for solar system composition
  gas, which can differ from that of higher metallicity gas.}.
They considered multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars, but did not favor any particular one.

>>>>

{\bf HD~20782/HD~20781:}
Two common proper motion G dwarf stars (G2/G9.5) with a projected separation of
$\sim9000$~AU (corresponding to 4.2\arcmin\ sky separation) and solar metallicity
host close-in giant planets.
HD~20782 hosts a Jupiter-mass planet on a very eccentric ($e\approx 0.97$)
orbit with a pericenter distance of 1.4~AU while HD~20781 hosts two
Neptune-mass planets within 0.3~AU with moderately high eccentricity
($e\sim0.1-0.3$).\footnote{
  The two stars were monitored by \project{HARPS} campaign, and it has recently
  been reported by \citealt{2017arXiv170505153U} that HD~20781 hosts four
  planets between $M\sin(i)\approx 0.006-0.04$~\mjupiter\ with $e \le 0.11$
  within $\approx 0.35$~AU.}
The measured abundances of 15 elements in the two stars are consistent
(\citealt{Mack:2014aa}).
However, \citealt{Mack:2014aa} argued that there is a moderately significant
($\sim 2\sigma$) positive slope of $\approx 10^{-5}$~dex\,K$^{-1}$ with
increasing \Tcondens\ for $\Tcondens>900$~K elements (namely, Na, Mn, Cr, Si,
Fe, Mg, Co, Ni, V, Ca, Ti, Al, Sc leaving out C and O of their measurements) in
the abundances of each star {\it individually}.
They suggest that this slope is evidence that the stars accreted
$10-20$~\mearth\ or \elem{H}-depleted rocky material during giant planet
migration.

{\bf HAT-P-1:}
A pair of G0 stars separated by 11\arcsec\ each with $\feh\approx0.15$ has
different planetary systems:
the secondary star is known to host one transiting giant planet
while no planet has been discovered around the primary star.
The two stars are identical
in metallicities and abundances for 23 elements measured with
the mean error of $0.013$~dex (\citealt{Liu:2014aa}).
Thus it seems that the presence of close-in giant planet does not necessarily
lead to atmospheric pollution of its host star.

{\bf HD~80606/HD~80607:}
Similar to HAT-P-1, no significant chemical difference between HD~80606 which
hosts a very eccentric ($e\approx0.94$) giant planet and HD~80607 which has no
detected planets are found in this pair of G5 stars with super-solar
metallicity ($\feh \approx 0.35$;\citealt{Saffe:2015aa,Mack:2016aa}).

{\bf XO-2N/XO-2S:}
A pair of G9 stars with super-solar metallicity ($\feh \gtrsim 0.35$),
each hosting planet(s):
XO-2N hosts a giant planet while XO-2S is known to host two giant planets with
masses $0.26 \mjupiter$ and $1.37 \mjupiter$ on moderately eccentric ($\approx
0.15$) orbits at $<0.5$~AU.
The system has received much attention due to
possibly the most robust and significant difference between the component stars
among those so far studied.
%TODO: check following with Biazzo+
All measured elements including \elem{Fe} are enhanced in XO-2N relative to
XO-2S, and the difference shows a significant correlation with \Tcondens\
(\citealt{Teske:2015aa,Ramirez:2015aa,Biazzo:2015aa} although see also
\citealt{Teske:2013aa}).
At low \Tcondens, volatile elements differ by $0.015$~dex while the range of
difference spans upto $0.1$~dex at $\Tcondens>1600$~K.

\citealt{Ramirez:2015aa} argued that the {\it depletion} of volatile elements
in XO-2S relative to XO-2N is plausibly due to the presence of {\it more} gas
giant planets around XO-2S, following a similar interpretation of
\citealt{Melendez:2009aa} of the trend between solar twins and the Sun.
In this scenario, forming planets in the protoplanetary disk are supposed to
``lock'' heavier elements to the core of gas giant planets as well as some
volatile elements in their envelopes. Then, the host star will accrete {\it
  gas} depleted in metals compared to their protostellar condition.
By tuning the metal content ($Z/X$) of gas giant planets and when the accretion
of gas occurs in terms of how much mass is in the convective envelop then, they
can match the mass difference of gas giant planets around each star, which is
at least $1~\mjupiter$.
On the positive correlation of $\Delta\elemH{X}$ with \Tcondens,
\citealt{Ramirez:2015aa} estimated that $20~\mearth$ of equal-part mixture of
Earth and CM chondrite-like material can explain the trend either as refractory
{\it depletion} in XO-2S due to {\it more} rocky planets around XO-2S, or
refractory enhancement in XO-2N by late time accretion in which case the
opposite would be true.

{\bf WASP-94A/WASP-94B:}
Each star in a pair of F8 and F9 stars with super-solar metallicity
($\feh\approx 0.3$) hosts a hot Jupiter.
The planet around WASP-94A is transiting with a misaligned, probably retrograde
circular ($e<0.13$) orbit, while that hosted by WASP-94B is a little more
massive by $\sim 0.15$~\mjupiter\ and closer in, aligned with the host star.
WASP-94A shows a depletion of $0.02$~dex in volatile and moderately volatile
elements ($\Tcondens < 1200$~K) and an enhancement of $0.01$~dex in refractory
elements ($\Tcondens>1200$~K) relative to WASP-94B, with a claimed median
uncertainty of $0.006$~dex among all elements
resulting in a statistically significant non-zero slope between
$\Delta\elemH{X}$ and $\Tcondens$ (\citealt{Teske:2016aa}).\footnote{
  %TODO: double check the following statement
  Note that the condensation
  temperature $\Tcondens$ used is for solar system composition
  gas, which can differ from that of higher metallicity gas.}
Multiple possibilities related to the formation and evolution
of planetary systems around each star as well as causes unrelated to planets
such as dust cleansing during the fully convective phase or different rotation
and granulation between the stars were considered, but none was favored.
